The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-14 paper.tex
update

First, we find that the simulated gamma-ray spectra are well fitted by\
the CRe spectral index 2.4 (the middle row),\
even simulated microwave spectra are marginally consistent with the observed.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane even the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\end{itemize}

>>>>

First, we find that the simulated gamma-ray spectra are well fitted by\
the CRe spectral index 2.4 (the middle row),\
despite the simulated microwave spectra are marginally consistent with the observed.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they have their origin around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}
